One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
Trivial changes.
Nai

The ever-changing nature of HPC has always compelled the HPC community to focus a lot of effort into training of new and existing practitioners. Historically, these efforts were tailored
 around a typical group of users possessing, due to their background, a certain set of programming skills. However, as HPC has become more diverse in terms of hardware, software and 
 the user background, the traditional training approaches became insufficient in addressing training needs of our community. This increasingly complicated HPC landscape makes 
 developement and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in 
 learning a particular set of skills? How can we satisfy their training needs if we don't really understand what these are? It's clear that HPC centres struggle to identify and overcome the 
 gaps in users' knowledge, while users struggle to identify skills required to perform their tasks.

@@

Most institutions operating HPC systems offer regular training events focusing on general aspects of their supercomputer's hardware architecture, software stack, application development environment  and various tuning and debugging tools.   
It is understandable why the materials they are geared towards the special demands of the institutions they support and its specific HPC environment. 
The problem is that teaching content typically covers only a small part of basic HPC skills necessary to use other HPC systems. 
This approach of teaching only specific implementations, tools or workflows, instead of concepts behind them makes a move to a different system or tool unnecessary complicated. 
Narrowing the scope of training events make sense from the HPC provider perspective, but is not very conducive to development of more comprehensive learning environment that provides assessment and certifies the newly acquired skills. So although, certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training. 
It is, however, clear that a certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,

>>>>

The ever-changing nature of HPC has always compelled the HPC community to focus a lot of effort into training of new and existing practitioners. Historically, these efforts were tailored
 around a typical group of users possessing, due to their background, a certain set of programming skills. However, as HPC has become more diverse in terms of hardware, software and
 the user background, the traditional training approaches became insufficient in addressing training needs of our community. This increasingly complicated HPC landscape makes
 development and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in
 learning a particular set of skills? How can we satisfy their training needs if we don't really understand what these are? It's clear that HPC centres struggle to identify and overcome the
 gaps in users' knowledge, while users struggle to identify skills required to perform their tasks.

@@

Most institutions operating HPC systems offer regular training events focusing on general aspects of their supercomputer's hardware architecture, software stack, application development environment  and various tuning and debugging tools.
It is understandable why the materials they are geared towards the special demands of the institutions they support and its specific HPC environment.
The problem is that teaching content typically covers only a small part of basic HPC skills necessary to use other HPC systems.
This approach of teaching only specific implementations, tools or workflows, instead of concepts behind them makes a move to a different system or tool unnecessary complicated.
Narrowing the scope of training events make sense from the HPC provider perspective, but is not very conducive to development of more comprehensive learning environment that provides assessment and certifies the newly acquired skills. So although, certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training.
It is, however, clear that a mapping of competences and certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
